\sysfull

### 2017-07-28 paper/evaluation.tex
Evalation section complete for now (will resume after experiments done)

\task{Check if the line of argument is solid for the above paragraphs about not selecting DINO, Memenos and Aplaca}{Brandon}

@@

Expected results:
\begin{itemize}
	\item comparison between manual (Chain code) and automatic taskification: in terms of code SLOCs, number of tasks, completion time (Chain), memory use (other metrics required?); 
	\item assessment of correctness (through manual inspection only?).
\end{itemize}

@@

Expected results:
\begin{itemize}
	\item Paging/memory experiment: page swapping cost (execution time)---comparing against chain and full double buffering approach, show number of page swaps,
\end{itemize}

@@

The final experiment assessing usefulness of \sys is its use in real application: battery-less microphone.

Expected results:
\begin{itemize}
	\item Compare execution time: \sys compared against Chain
\end{itemize}

\todo{Provide results and text to this section---if time allows (this result is not critical)}{Amjad/Przemek}

>>>>

\todo{Check if the line of argument is solid for the above paragraphs about not selecting DINO, Memenos and Aplaca}{Brandon}

@@

Expected results:
\begin{itemize}
	\item comparison between manual (Chain code) and automatic taskification: in terms of code SLOCs, number of tasks, completion time (Chain), memory use (other metrics required?)
	\item assessment of correctness (through manual inspection only?).
\end{itemize}

@@

Expected results:
\begin{itemize}
	\item page swapping cost in terms of execution time: compare against Chain and full double buffering approach; show number of page swaps---do the experiment for all applications
\end{itemize}

@@

The final experiment assessing usefulness of \sys's use in real application. For this we have a implemented an battery-less wirelessly-powered sound detector as an example. To the best of our knowledge, this is the first case study that demonstrates a intermittently-powered system supplied by harvested energy at runtime, which continuously interacts with real-life signals.

The application aims at detecting a specific tone in the audio signal (in the implementation: 1\,kHz) based on on-the-fly audio measurement. For this we have connected an analog MEMS microphone~\cite{microphone} output to AUX3 port of WISP\,5.1 (while the microphone was powered directly by WISP, which was then wirelessly power-supplied by the RFID reader). Audio signal is sampled by the microcontroller's ADC and passed to the FFT function (internal function of the TI's Digital Signal Processing library~\cite{ti_dsp}) to find a tone above a predefined threshold. The output of the detection is signalled by the WISP on-board LED. The video of demonstrating the working system is available via \url{https://link_to_a_video}.

Expected results:
\begin{itemize}
	\item Compare execution time: \sys against Chain for X\,s long audio signal detection at two antenna distances
	\item Make a video of the demonstration 
\end{itemize}

\todo{Check if we really need this application}{Brandon}
\todo{Provide results and text to this section---if time allows (this result is not critical)}{Amjad/Przemek}
